Spatial Analysis

### 2021-10-04 Scripts/spatial_analisis.Rmd
Interpolation figure

inter_map <- ggplot() +
   geom_tile(data = subset(interpol_result, mean_cpue == 0),
            aes(
              x = lon,
              y = lat
            ),
            fill = "grey90",
              color = "grey90"
  ) + 
  geom_tile(data = subset(interpol_result, mean_cpue > 0),
            aes(
              x = lon,
              y = lat,
              fill = mean_cpue,
              color = mean_cpue
            )
  ) + 
  geom_point(data = centroid_db,
            aes(
              x = lon,
              y = lat
            ),
            shape = 3,
            color = "white"
  ) + 
  geom_sf(data = land_sf,aes()) +
  labs(x = "Longitude",
         y = "Latitude") +
  # ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
  #                                  size = 4,
  #                                  box.padding = 0.10,
  #                                  hjust = 1) +
  scale_fill_viridis("Mean Interpolation", alpha = 0.8,
                     limits = c(0,40)) +
  scale_color_viridis("Mean Interpolation", alpha = 0.8, 
                      limits = c(0,40)) +
  facet_grid(label ~ spp) +
  my_ggtheme_m(map_type = "na", leg_pos = "bottom",ax_tx_s = 10,ax_tl_s = 12,leg_tx_s = 12) +
  theme(legend.key.width = unit(3,"line"))

ggsave("interpolation_fig.jpg",
       inter_map,
       path = my_path("R","Figures"),
       width = 8,
       height = 6)
```

>>>>

inter_map <- ggplot() +
   geom_tile(data = subset(interpol_result, mean_cpue == 0),
            aes(
              x = lon,
              y = lat
            ),
            fill = "grey90",
              color = "grey90"
  ) + 
  geom_tile(data = subset(interpol_result, mean_cpue > 0),
            aes(
              x = lon,
              y = lat,
              fill = mean_cpue,
              color = mean_cpue
            )
  ) + 
  geom_point(data = centroid_db,
            aes(
              x = lon,
              y = lat
            ),
            shape = 3,
            color = "white"
  ) + 
  geom_sf(data = land_sf,aes()) +
  labs(x = "Longitude",
         y = "Latitude") +
  # ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
  #                                  size = 4,
  #                                  box.padding = 0.10,
  #                                  hjust = 1) +
  scale_fill_viridis("Mean\nInterpolation",
                     limits = c(0,40)) +
  scale_color_viridis("Mean\nInterpolation",
                      limits = c(0,40)) +
  facet_grid(spp~label) +
  my_ggtheme_m(map_type = "na", leg_pos = "right",ax_tx_s = 7,ax_tl_s = 10,leg_tx_s = 10) #+
  # theme(legend.key.width = unit(3,"line"))

ggsave("interpolation_fig.jpg",
       inter_map,
       path = my_path("R","Figures"),
       width = 6,
       height = 6)
```
